**Machine learning identifies unique taxa differentiating proximal and distal

### 2017-06-13 submission/manuscript.Rmd
rmd updates

\newpage
\linenumbers
```{r dependencies}
pack_used <- c('randomForest','ggplot2', 'pROC', 'knitr','dplyr','AUCRF', 'tidyr', 'caret', 'RColorBrewer', 'reshape2', 'wesanderson')
for (dep in pack_used){
  if (dep %in% installed.packages()[,"Package"] == FALSE){
    install.packages(as.character(dep), repos = 'http://cran.us.r-project.org', 
                     quiet=TRUE);
  }
  library(dep, verbose=FALSE, character.only=TRUE)
}
```

```{r datasets}
meta <- 'data/raw/kws_metadata.tsv'
shared <- 'data/mothur/kws_final.an.shared'
tax <- 'data/mothur/kws_final.an.cons.taxonomy'
subsample <- 'data/mothur/kws_final.an.0.03.subsample.shared'

meta_file <- read.table(file='data/raw/kws_metadata.tsv', header = T)
shared_file <- read.table(file='data/mothur/kws_final.an.shared', sep = '\t', header=T, row.names=2)
tax_file <- read.table(file='data/mothur/kws_final.an.cons.taxonomy', sep = '\t', header=T, row.names=1)
shared_meta <- merge(meta_file, shared_file, by.x='group', by.y='row.names')

simps <- read.table(file='data/mothur/kws_final.an.groups.summary', header = T)
metasimp <- merge(metadata, simps)

@@

```{r otu_barplot}
source('code/Sum_OTU_by_Tax.R')
source('code/sum_shared.R')

@@

```{r simpson}

>>>>

\newpage
\linenumbers

```{r dependencies}
#setwd('~/Documents/Flynn_LRColon_XXXX_2017')
pack_used <- c('randomForest','ggplot2', 'pROC', 'knitr','dplyr','AUCRF', 'tidyr', 'caret', 'RColorBrewer', 'reshape2', 'wesanderson')
for (dep in pack_used){
  if (dep %in% installed.packages()[,"Package"] == FALSE){
    install.packages(as.character(dep), repos = 'http://cran.us.r-project.org', 
                     quiet=TRUE);
  }
  library(dep, verbose=FALSE, character.only=TRUE)
}
```

```{r datasets}
#setwd("~/Users/kaitlinflynn/Documents/Flynn_LRColon_XXXX_2017")
meta <- '../data/raw/kws_metadata.tsv'
shared <- '../data/mothur/kws_final.an.shared'
tax <- '../data/mothur/kws_final.an.cons.taxonomy'
subsample <- '../data/mothur/kws_final.an.0.03.subsample.shared'

meta_file <- read.table(file='../data/raw/kws_metadata.tsv', header = T)
shared_file <- read.table(file='../data/mothur/kws_final.an.shared', sep = '\t', header=T, row.names=2)
tax_file <- read.table(file='../data/mothur/kws_final.an.cons.taxonomy', sep = '\t', header=T, row.names=1)
shared_meta <- merge(meta_file, shared_file, by.x='group', by.y='row.names')

simps <- read.table(file='../data/mothur/kws_final.an.groups.summary', header = T)
simpmeta <- merge(meta_file, simps)

tyc <- read.table("../data/mothur/kws_final.an.summary", sep = '\t', header = T, row.names=NULL)

@@

```{r otu_barplot}
source('../code/Sum_OTU_by_Tax.R')
source('../code/sum_shared.R')

@@
